Data Specialization for a Staged Lambda Calculus

### 2015-02-26 paper/splitting.tex
More tweaks to 2-splitting.  Now actually moving on to 1M

\textbf{\bbtwo\ term splitting.}  For any $\coltwo e A$ which reduces
to a residual $q$ (via $\diatwo e q$) and then a final value $v$ (via
$\reduce q v$), splitting $e$ (via the new relation~$\splittwosym$)
yields a pair of monostaged terms $p$ (containing first stage
computations in $e$) and $l.r$ (containing second stage computations
in $e$). Executing $p$ in a first pass produces $b$ (via $\reduce p
b$). Then, in a second pass, $\reduce {[b/l]r} {v'} = v$.  Since
execution of the first pass serves to generate input for the second
pass, we say $p$ is a {\em precomputation} that produces a {\em
  boundary value} ($b$) that is communicated to the {\em resumer}
($l.r$).

The process of splitting \bbtwo\ terms is given by via the new
relation~$\splittwosym$.

>>>>

\textbf{\bbtwo\ term splitting.}  For any $\coltwo e A$ which reduces
to a residual $q$ (via $\diatwo e q$) and then a final value $v$ (via
$\reduce q v$), splitting $e$ (via the new relation~$\splittwosym$)
yields a pair of monostaged terms $p$ (containing all first stage
computations in $e$) and $l.r$ (containing all second stage
computations in $e$). Executing $p$ in a first pass produces $b$ (via
$\reduce p b$). Then, in the second pass, $\reduce {[b/l]r} {v'} = v$.
Since execution of the first pass serves to generate input for the
second pass, we say $p$ is a {\em precomputation} that produces a {\em
  boundary value} ($b$) for the {\em resumer} ($l.r$).

% The process of splitting \bbtwo\ terms is given by via the new
% relation~$\splittwosym$.
